Identifiers for Iterative Forecasting

### 2022-12-01 README.Rmd
patch

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![CRAN status](https://www.r-pkg.org/badges/version/contentid)](https://CRAN.R-project.org/package=contentid)
[![R build status](https://github.com/cboettig/contentid/workflows/R-CMD-check/badge.svg)](https://github.com/cboettig/contentid/actions)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![CRAN status](https://www.r-pkg.org/badges/version/contentid)](https://CRAN.R-project.org/package=contentid)
[![R-CMD-check](https://github.com/cboettig/contentid/workflows/R-CMD-check/badge.svg)](https://github.com/cboettig/contentid/actions)
<!-- badges: end -->

### 2022-12-01 inst/examples/benchmarking-backends.Rmd
patch

df <- dplyr::select(df, url = contentURL, id = checksum)
ex <- sample(df$url, 1e6)
```

@@

```{r disk.frame}
df_con <- disk.frame::as.disk.frame(df)
bench::bench_time({ ##
  id3 <- df_con %>% filter(url %in% ex) %>% collect() %>% pull(id)
})

>>>>

df <- dplyr::select(df, url = contentURL, id = checksum)
ex <- sample(df$url, 1e3)
```

@@

```{r disk.frame}
df_con <- disk.frame::as.disk.frame(df)
bench::bench_time({ ##
  id3 <- df_con %>% filter(url %in% ex) %>% pull(id)
})

### 2022-12-01 paper/paper.Rmd
patch

print(c(delta_catch_id=delta_catch_id, 
        delta_taxa_id=delta_taxa_id,
        delta_effort_id=delta_effort_id, 
        delta_sites_id=delta_sites_id))
```
```{r contentid-remote-build, eval=FALSE, include=FALSE}
delta_catch_id <- 'hash://sha1/317d7f840e598f5f3be732ab0e04f00a8051c6d0'
delta_catch_id <- 'hash://sha256/e0dc10d7f36cfc5ac147956abb91f24f2b2df9f914a004bbf1e85e7d9cf52f41'
delta_taxa_id <- 'hash://sha1/1bf0da8443e5bf8c9e7d16bf715a33129c9ff169'
delta_taxa_id <- 'hash://sha256/1473de800f3c5577da077507fb006be816a9194ddd417b1b98836be92eaea49d'
delta_effort_id <- 'hash://sha256/f2433efab802f55fa28c4aab628f3d529f4fdaf530bbc5c3a67ab92b5e8f71b2'
delta_sites_id <- 'hash://sha256/e25498ffc0208c3ae0e31a23204b856a9309f32ced2c87c8abcdd6f5cef55a9b'
```

>>>>

print(c(delta_catch_id=delta_catch_id, 
        delta_taxa_id=delta_taxa_id,
        delta_effort_id=delta_effort_id, 
        delta_sites_id=delta_sites_id))
```

Accessing a data file using a URL or file path creates a certain degree of ambiguity from a reproducibility and provenance perspective. 
Is the intent of the code to read in the "latest version" of whatever content is found at that address, or has the code been written with the assumption that it is recieving exactly the same input every time?
Content-based identifiers provide a mechanism for code to be more explicit on this point. 
Instead of writing out an ambiguous URL or filepath into the script, we can explicitly embed the content hash, using variable assighment to give the opaque hash a more convenient alias:

```{r contentid-remote-build, eval=FALSE, include=FALSE}
delta_catch_id <- 'hash://sha1/317d7f840e598f5f3be732ab0e04f00a8051c6d0'
delta_catch_id <- 'hash://sha256/e0dc10d7f36cfc5ac147956abb91f24f2b2df9f914a004bbf1e85e7d9cf52f41'
delta_taxa_id <- 'hash://sha1/1bf0da8443e5bf8c9e7d16bf715a33129c9ff169'
delta_taxa_id <- 'hash://sha256/1473de800f3c5577da077507fb006be816a9194ddd417b1b98836be92eaea49d'
delta_effort_id <- 'hash://sha256/f2433efab802f55fa28c4aab628f3d529f4fdaf530bbc5c3a67ab92b5e8f71b2'
delta_sites_id <- 'hash://sha256/e25498ffc0208c3ae0e31a23204b856a9309f32ced2c87c8abcdd6f5cef55a9b'
```
